nextflu: Real-time tracking of seasonal influenza virus evolution in humans

### 2015-04-07 manuscript/nextflu.tex
Fix references to conform to Bioinformatics et al. format.

\begin{figure}[t!]
	\begin{center}
	\includegraphics[width=0.99\columnwidth]{figures/tree}
\caption[]{The \nextflu{} website with the user interface on the left and
the phylogenetic tree on the right.}
\label{fig:tree}
\end{center}
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=0.99\columnwidth]{figures/frequencies}
\caption[]{The frequency diagram allows geography-specific plotting of frequencies of individual mutations, pairs of mutations and clades in the tree.}
\label{fig:freq}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{nextflu}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.99\columnwidth]{figures/tree}
	\caption[]{The \nextflu{} website with the user interface on the left and the phylogenetic tree on the right.}
	\label{fig:tree}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.99\columnwidth]{figures/frequencies}
	\caption[]{The frequency diagram allows geography-specific plotting of frequencies of individual mutations, pairs of mutations and clades in the tree.}
	\label{fig:freq}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{}

\bibitem[Bastien {\em et~al.}, 2010]{bastien_human_2010}
Bastien,N. {\em et~al.} (2010{\em{}})
  Human infection with a triple-reassortant swine influenza {A (H1N1)} virus
  containing the hemagglutinin and neuraminidase genes of seasonal influenza
  virus.
\newblock {\em J Infect Dis, } {\bf 201} (8), 1178--1182.

\bibitem[Bogner {\em et~al.}, 2006]{GISAID}
Bogner,P. {\em et~al.} (2006{\em{}}) A global
  initiative on sharing avian flu data.
\newblock {\em Nature, } {\bf 442} (7106), 981--981.

\bibitem[Bostock {\em et~al.}, 2011]{bostock_d3_2011}
Bostock,M. {\em et~al.} (2011{\em{}}) D$^3$: data-driven
  documents.
\newblock {\em IEEE Trans Vis Comput Graphics, } {\bf 17} (12), 2301--2309.

\bibitem[Katoh and Standley, 2013]{katoh_mafft_2013}
Katoh,K. and Standley,D.M. (2013{\em{}}) {MAFFT} multiple sequence alignment
  software version 7: improvements in performance and usability.
\newblock {\em Mol Biol Evol, } {\bf 30}, 772--780.

\bibitem[Koel {\em et~al.}, 2013]{koel_substitutions_2013}
Koel,B.F. {\em et~al.} (2013{\em{}})
  Substitutions near the receptor binding site determine major antigenic change
  during influenza virus evolution.
\newblock {\em Science, } {\bf 342} (6161), 976--979.

\bibitem[\L{}uksza and L\"a{}ssig, 2014]{luksza_predictive_2014}
\L{}uksza,M. and L\"a{}ssig,M. (2014{\em{}}) A predictive fitness model for
  influenza.
\newblock {\em Nature, } {\bf 507} (7490), 57--61.

\bibitem[Neher {\em et~al.}, 2014]{neher_predicting_2014}
Neher,R.A. {\em et~al.} (2014{\em{}}) Predicting evolution
  from the shape of genealogical trees.
\newblock {\em eLife Sciences, } {\bf 3}, e03568.

\bibitem[Oliphant, 2007]{oliphant_python_2007}
Oliphant,T. (2007{\em{}}) Python for scientific computing.
\newblock {\em Comput Sci Eng, } {\bf 9} (3), 10--20.

\bibitem[Price {\em et~al.}, 2009]{price_fasttree_2009}
Price,M.N. {\em et~al.} (2009{\em{}}) {FastTree:} computing
  large minimum evolution trees with profiles instead of a distance matrix.
\newblock {\em Mol Biol Evol, } {\bf 26} (7), 1641--50.

\bibitem[Stamatakis, 2014]{stamatakis_raxml_2014}
Stamatakis,A. (2014{\em{}}) {RAxML} version 8: a tool for phylogenetic analysis
  and post-analysis of large phylogenies.
\newblock {\em Bioinformatics, } {\bf 30} (9), 1312--1313.

\bibitem[{World Health Organization}, 2009]{flufactsheet}
{World Health Organization} (2009{\em{}}) {\em {Influenza Fact sheet}}.
\newblock Available at http://www.who.int/mediacentre/factsheets/fs211/en/.

\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
